---
title: "Reproducible Research: Peer Assessment 1"
author: "J Go"
date: "June 5, 2016"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
### fork/clone the Coursera repository
### manually fork course project 1 from course github to personal github
```
Open Safari web browser
Login to my github account at https://github.com/JGoDC/
Open another tab for coursera course repo at:
http://github.com/rdpeng/RepData_PeerAssessment1
Click on fork on course github repo page in browser
Select proper destination since a choice exists
Now have forked repo at:
https://github.com/JGoDC/RepData_PeerAssessment1
```
### manually clone course project 1 from github to local machine
```
$ cd ~/coursera/r
$ git clone https://github.com/JGoDC/RepData_PeerAssessment1
Now have cloned repo in new directory on local machine with following files:
~/coursera/r/RepData_PeerAssessment1
drwxr-xr-x  3 j  staff    102 Jun  2 20:34 instructions_fig
drwxr-xr-x  3 j  staff    102 Jun  2 20:34 doc
-rw-r--r--  1 j  staff  53559 Jun  2 20:34 activity.zip
-rw-r--r--  1 j  staff   7776 Jun  2 20:34 README.md
-rw-r--r--  1 j  staff    358 Jun  2 20:34 PA1_template.Rmd
```
### note clone date and time from timestamp on files
```
Jun 02, 2016, 20:34 EST
```
### examine current directory and current files
```{r examine_current_dir_and_files}
getwd()
dir(full.names = TRUE, recursive = TRUE)
```
### check for "data" directory, create if necessary
```{r check_existence_data_dir}
data_dir="./data"
if (!file.exists(data_dir)) {
    dir.create(data_dir)
} else {
    cat('data dir exists: [', data_dir, ']', '\n')
}
```

### check for activity.csv file, unzip activity.zip into data dir if necessary
```{r check_existence_file_activity.csv}
data_file <- paste0(file.path(".", "data", "activity.csv"))
if(!file.exists(data_file)) {
        zip_file <- "activity.zip"
        unzip(zip_file, exdir = data_dir )
} else {
    cat('data file exists: [', data_file, ']', '\n')
}
```

### read input data file with read.csv
```{r read_input_data}
dat <- read.csv(data_file)
```

## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
